Interval-Valued Quantum Probabilities: Contextuality and the Born Rule

### 2017-05-18 prop_letter.tex
prop_letter.tex \section{Kochen-Specker} Add Choquet integral citation

The expectation value is intuitively between two possible outcomes
which lie between the minimum and maximum bounds of the given
probability intervals. If the QIVPM is crypto-deterministic, this
interval collapses to a singleton $\left\{ \lambda\right\} $, where
$\lambda$ is an eigenvalue of $\mathbf{O}$. If we define the
multiplication of two singleton sets~$\left\{ \lambda_{1}\right\} $
and $\left\{ \lambda_{2}\right\} $ to be
$\left\{ \lambda_{1}\lambda_{2}\right\} $, then we have
\begin{equation}
\prod_{j=1}^{N}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{N}\mathbf{O}_{j}}_{\bar{\mu}}\label{eq:Kochen-Specker-Rules}
\end{equation}
for any sequence of commuting observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{N}$.

>>>>

The expectation value is intuitively between two possible outcomes
which lie between the minimum and maximum bounds of the given
probability intervals, and this definition also consistent with the classical
Choquet integral on commuting sub-event space by adopting the classical
theorem~\cite{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}.
If the QIVPM is crypto-deterministic, this
interval collapses to a singleton $\left\{ \lambda\right\} $, where
$\lambda$ is an eigenvalue of $\mathbf{O}$. If we define the
multiplication of two singleton sets~$\left\{ \lambda_{1}\right\} $
and $\left\{ \lambda_{2}\right\} $ to be
$\left\{ \lambda_{1}\lambda_{2}\right\} $, then we have
\begin{equation}
\prod_{j=1}^{N}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{N}\mathbf{O}_{j}}_{\bar{\mu}}\label{eq:Kochen-Specker-Rules}
\end{equation}
for any sequence of commuting observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{N}$.
